Indirect Conflicts: An Exploration and Discussion of Tools, Process, and Developer Insight

### 2013-11-07 iced-2013/paper.tex
ICED evaluation is in. Not sure how much to write there.

Following our data collection and analysis, we re-interviewed some of our initial interview participants
in order to validate our findings. We confirmed our hypotheses as to whether or not they resonate with 
industry participants' opinions and experiences regarding indirect conflicts and as to their industrial 
applicability. Due to limited time constraints of the interviewed participants, we could only re-interview
five participants. Those that were re-interviewed came from the range of 5-10 years of software development
experience. Re-interviewed participants were given our 3 research questions along with results and 9 findings,
and asked open ended questions regarding their opinions and experiences to validate our findings. The five
participants found FILL IN HERE WHEN COMPLETE.

@@

>>>>

Following our data collection and analysis, we re-interviewed some of our initial interview participants
in order to validate our findings. We confirmed our findings as to whether or not they resonate with 
industry participants' opinions and experiences regarding indirect conflicts and as to their industrial 
applicability. Due to limited time constraints of the interviewed participants, we could only re-interview
five participants. Those that were re-interviewed came from the range of 5-10 years of software development
experience. Re-interviewed participants were given our 3 research questions along with results and main
discussion points, and asked open ended questions regarding their opinions and experiences to validate our 
findings. We also evaluated our grounded theory approach as per Corbin and Strauss'~\cite{Corbin:1998:SP}
list of criteria to evaluate quality and credibility. This evaluation can be seen in Section~\ref{sec:eval}

@@

From the re-interviewed participants, we found extremely positive feedback regarding both our results and major discussion
points. Participants often had new stories and experiences to share once they had heard the results of this paper which
confirmed the findings and often were quite shocked to hear the results as they did not usually think about their actions
as such but then realized the results held true to their daily actions for better or worse.
